ChemKED: a human- and machine-readable data standard for chemical kinetics experiments

### 2017-10-02 pyked.tex
Add all possible keys to YAML section
We were only missing a few anyways...

The second section of the file encodes the experimental data as a sequence of mappings. The
top-level key for the sequence is called \yabox|datapoints|. For the current version of the \ck{}
schema, only autoignition delay experiments are supported. The following information os required in
each element of the sequence:
%
\begin{itemize}
    \item \yabox|temperature| (required, sequence): The temperature of the
    experiment, with units and optionally uncertainty
    \item \yabox|ignition-delay| (required, sequence): The ignition delay of the
    experiment, with units and optionally uncertainty
    \item \yabox|pressure| (required, sequence): The pressure of the experiment,
    with units and optionally uncertainty
    \item \yabox|composition| (required, mapping): The composition of the
    mixture in the experiment, described via a nested mapping with the fields
    \begin{itemize}
        \item \yabox|kind| (required, string): one of \yabox|mole fraction|, \yabox|mole percent|, or \yabox|mass fraction|
        \item \yabox|species|: sequence of mappings, with the fields
        \begin{itemize}
            \item \yabox|species-name| (required, string): The name of the species
            \item \yabox|amount| (required, sequence): The mole fraction or percent, or the mass fraction, optionally with uncertainty
            \item \yabox|InChI|, \yabox|SMILES|, \yabox|atomic-composition|, or
            \yabox|elemental-composition| (required, string or sequence): The InChI
            or SMILES string representing the molecule, or its atomic or elemental
            composition (\yabox|atomic-composition| and\\
            \yabox|elemental-composition| are synonyms) as a sequence
        \end{itemize}
    \end{itemize}
    \item \yabox|ignition-type| (required, mapping): The method used to detect
    ignition in the experiments. The required fields are
    \begin{itemize}
        \item \yabox|type| (required, string): How ignition delay was
        measured; one of \yabox|d/dt max| (indicates the ignition point was
        found at the maximum of the time derivative of the \yabox|target|),
        \yabox|max| or \yabox|min| (indicates the ignition point was at the
        maximum or minimum of the \yabox|target|), \yabox|1/2 max| (
        indicates the half-maximum point of \yabox|target|), or \yabox|d/dt max extrapolated|
        (indicates the maximum slope of the target extrapolated to the baseline)
        \item \yabox|target| (required, string): The target for the ignition
        \yabox|type| measurement; one of \yabox|temperature|, \yabox|pressure|,
        \yabox|OH|, \yabox|OH*|, \yabox|CH|, or \yabox|CH*|
    \end{itemize}
\end{itemize}

The top-level key for the sequence is called \yabox|datapoints|. Each of the
quantities in an element must be specified with units. This should be done as a
single string associated with the first element of the sequence. The units of
the quantity are validated to ensure appropriate dimensionality
for the quantity. In addition, each of the quantities in an element can
optionally be assigned an uncertainty. This uncertainty can be either absolute
or relative, and is specified as an element of the sequence of the associated key.
For example, the absolute uncertainty of the temperature and the relative
uncertainty of the ignition delay might be specified as:
%
\begin{yamlbox}
datapoints:
  - temperature:
      - 1100 kelvin
      - uncertainty-type: absolute
        uncertainty: 10 kelvin
    ignition-delay:
      - 10 us
      - uncertainty-type: relative
        uncertainty: 0.1
    ...
\end{yamlbox}

@@

>>>>

The second section of the file encodes the experimental data as a sequence of mappings. The
top-level key for the sequence is called \yabox|datapoints|. For the current version of the \ck{}
schema, only autoignition delay experiments are supported. The following information os required in
each element of the sequence:
%
\begin{itemize}
    \item \yabox|temperature| (required, sequence): The temperature of the
    experiment, with units and optionally uncertainty
    \item \yabox|ignition-delay| (required, sequence): The ignition delay of the
    experiment, with units and optionally uncertainty
    \item \yabox|pressure| (required, sequence): The pressure of the experiment,
    with units and optionally uncertainty
    \item \yabox|first-stage-ignition-delay| (optional, sequence): If two stages of ignition are
    present in the experiment, this is the length of the first stage of ignition, and the
    \yabox|ignition-delay| is then the overall ignition delay
    \item \yabox|equivalence-ratio| (optional, float): The value of the equivalence ratio
    \item \yabox|composition| (required, mapping): The composition of the
    mixture in the experiment, described via a nested mapping with the fields:
    \begin{itemize}
        \item \yabox|kind| (required, string): one of \yabox|mole fraction|, \yabox|mole percent|, or \yabox|mass fraction|
        \item \yabox|species|: sequence of mappings, with the fields:
        \begin{itemize}
            \item \yabox|species-name| (required, string): The name of the species
            \item \yabox|amount| (required, sequence): The mole fraction or percent, or the mass fraction, optionally with uncertainty
            \item \yabox|InChI|, \yabox|SMILES|, \yabox|atomic-composition|, or
            \yabox|elemental-composition| (required, string or sequence): The InChI
            or SMILES string representing the molecule, or its atomic or elemental
            composition (\yabox|atomic-composition| and\\
            \yabox|elemental-composition| are synonyms) as a sequence
        \end{itemize}
    \end{itemize}
    \item \yabox|ignition-type| (required, mapping): The method used to detect
    ignition in the experiments. The required fields are
    \begin{itemize}
        \item \yabox|type| (required, string): How ignition delay was
        measured; one of \yabox|d/dt max| (indicates the ignition point was
        found at the maximum of the time derivative of the \yabox|target|),
        \yabox|max| or \yabox|min| (indicates the ignition point was at the
        maximum or minimum of the \yabox|target|), \yabox|1/2 max| (
        indicates the half-maximum point of \yabox|target|), or \yabox|d/dt max extrapolated|
        (indicates the maximum slope of the target extrapolated to the baseline)
        \item \yabox|target| (required, string): The target for the ignition
        \yabox|type| measurement; one of \yabox|temperature|, \yabox|pressure|,
        \yabox|OH|, \yabox|OH*|, \yabox|CH|, or \yabox|CH*|
    \end{itemize}
\end{itemize}

Each of the
quantities in an element must be specified with units. This should be done as a
single string associated with the first element of the sequence. The units of
the quantity are validated to ensure appropriate dimensionality
for the quantity. In addition, each of the quantities in an element can
optionally be assigned an uncertainty. This uncertainty can be either absolute
or relative, and is specified as an element of the sequence of the associated key.
For example, the absolute uncertainty of the temperature and the relative
uncertainty of the ignition delay might be specified as:
%
\begin{yamlbox}
datapoints:
  - temperature:
      - 1100 kelvin
      - uncertainty-type: absolute
        uncertainty: 10 kelvin
    ignition-delay:
      - 10 us
      - uncertainty-type: relative
        uncertainty: 0.1
    ...
\end{yamlbox}

@@

\subsubsection{Shock Tube Experiments}\label{sec:shock-tube-experiments}

There is one additional key that can be used to describe the facility-specific effects during a
shock tube experiment:
%
\begin{itemize}
    \item \yabox|pressure-rise| (optional, sequence): The pressure rise in the driven section after
    the passage of the reflected shock, in dimensions of inverse time. Must include units and,
    optionally, uncertainty
\end{itemize}

\subsubsection{Rapid Compression Machine Experiments}\label{sec:rcm-experiments}

Rapid compression machine experiments typically report several additional pieces of information in
addition to the ignition delay. As for shock tube experiments, these describe some of the
facility-specific effects during an experiment. The keys to describe this information are:
%
\begin{itemize}
    \item \yabox|volume-history| (optional, mapping): Specify the volume history of the reaction
    chamber as a function of time during a rapid compression machine experiment. The fields in this
    mapping are:
    \begin{itemize}
        \item \yabox|volume| (required, mapping): A mapping describing the volume in the history.
        The fields in this mapping are:
        \begin{itemize}
            \item \yabox|units| (required, string): the units of the volume, with dimensions length
            cubed
            \item \yabox|column| (required, integer): the 0-based index of the column storing the
            volume information in the \yabox|values| array
        \end{itemize}
        \item \yabox|time| (required, mapping): A mapping describing the time in the history.
        The fields in this mapping are:
        \begin{itemize}
            \item \yabox|units| (required, string): the units of the time
            \item \yabox|column| (required, integer): the 0-based index of the column storing the
            time information in the \yabox|values| array
        \end{itemize}
        \item \yabox|values| (required, sequence): A sequence of sequences describing the values of
        the volume at the time points.
    \end{itemize}
    \item \yabox|compressed-temperature| (optional, sequence): The estimated temperature at the end
    of the compression stroke
    \item \yabox|compression-time| (optional, sequence): The time taken during the compression
    stroke
    \item \yabox|compressed-pressure| (optional, sequence): The measured pressure at the end of the
    compression stroke
\end{itemize}

\subsection{Public Database of \ck{} Files}\label{sec:public-database}
